Rising from the Ashes II.: something something

### 2024-08-30 paper/ms.tex
Title updates
Update abstract

\shorttitle{The Milky Way's Phoenix Phase}
\shortauthors{Beane et al.}

@@

\title{Something something}

@@

\begin{abstract}
    The Milky Way is known to host at least two modes in the present day distribution of chemical abundances. The exact cause of this bimodality is disputed, but one class of explanations involves the merger between the Milky Way and a relatively massive sattelite (Gaia-Sausage-Enceladus) at $z\sim2$. However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalance, morphology, and mechanism behind multimodality. We present a case study of a galaxy at $z=1.5$ in the Illustris TNG50 simulation which undergoes a starburst and brief quiescent phase. In the fiducial simulation, this galaxy does not host any multimodality in its chemical abundance plane. However, when an artificial slope in \alphaFe{} as a function of time is added (older stars are given boosted \alphaFe{}), we show that the distribution becomes strikingly multimodal. This suggests that, for this creation avenue, multimodality can only be created at times when \alphaFe{} is rapidly declining, as expected at high-$z$. It also provides additional support that models must produce galaxies with this declination. We suggest that TNG50 fails in this respect because the resolved star formation efficiency at high densities is too low.
  \end{abstract}

>>>>

\shorttitle{Something Something}
\shortauthors{Beane et al.}

@@

\title{Rising from the Ashes II.: something something}

@@

\begin{abstract}
    The Milky Way is known to host at least two modes in the present day distribution of chemical abundances. The exact cause of this bimodality is disputed, but one class of explanations involves the merger between the Milky Way and a relatively massive sattelite (Gaia-Sausage-Enceladus) at $z\sim2$. However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalance, morphology, and mechanism behind multimodality. We present a case study of a subhalo at $z=1.5$ in the Illustris TNG50 simulation which undergoes a starburst and brief quiescent phase. After a minor post-processing step which boosts the \alphaFe{} of old star particles, we demonstrate that this galaxy hosts a strongly bimodal distribution in the \alphaFe{}-\FeH{} plane. The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period. The quiescent period in this galaxy is not associated with a merger but some unspecified internal process. We argue that the requisite $\alpha$-boosting, post-processing step can be understood as the TNG model underproducing SF in the densest regions at high-$z$.
  \end{abstract}
